### 2018-06-29 FrascatiPlot/Paper/NucleiB2.tex
Appendix B updated, together with text in the coalescence part and table caption. Now breaking for lunch & train

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced (see text and Appendix \ref{appendix:Sato} for details). References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

@@

In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.

@@

\begin{equation}
 \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
\end{equation}

@@

\begin{equation}
 {\rm rms}_{A}^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
\end{equation}

\noindent for point-like constituents. In particular, we obtain $r_{d}=\sqrt{4/3}{\rm rms}_{d}$ for A= 2, $r_{3}= {\rm rms}_{3}$ for A = 3, and ???????.

@@

%%%%%%%%APPENDIX
\begin{appendix}
\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
As discussed in~\cite{Nagle:1996vp}, the approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}. Moreover, the approach of \cite{Sato:1981ez} assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (as those introduced by the presence of hydrodynamical flow).

For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals

\begin{equation}
	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
\end{equation}

\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$.

The coalescence process in~\cite{Sato:1981ez} is formulated in terms of the momentum per nucleon $p_{p,n}$ and thus it relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as

@@

\noindent Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter

\begin{eqnarray}
B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} {1 \over m^{A-1}} {1 \over A^{2}}  \\
           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{3(A-1)/2} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{3(A-1)/2} \;,
\end{eqnarray}

\noindent where $\nu_{A}$ corresponds again to the size parameter of the gaussian wave-function of the nucleus which are assumed as gaussians (solutions to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:

\begin{equation}
 \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
\end{equation}

\noindent with an appropriate normalisation factor $C$. The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius $r_{A}^{rms}$ is reproduced. The relation between $r_{A}^{rms}$ and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration. In particular, one obtains for A < 5:

\begin{eqnarray}
	(A = 2) \;\;  \nu_{d} = {2 \over r_{d}^2} = {3 \over 4 {r_{d}^{rms}}^2 }  \\
	(A = 3) \;\;  \nu_{t,{\rm 3He}} = {1 \over r_{t,{\rm 3He}}^2} = {1 \over {r_{t,{\rm 3He}}^{rms}}^2 } \\
	(A = 4)  \;\; \nu_{\alpha} =  {9 \over 8{r_{\rm 4He}^{rms}}^2 }
\end{eqnarray}

\noindent Please note that proton rms charge radius ${r_{p}^{rms}}$ is subtracted quadratically from the measured rms charge radius ${r_{A}^{rms,meas}}$ of the nucleus ${r_{A}^{rms}} = \sqrt{{r_{A}^{rms,meas}}^2 - {r_{p}^{rms}}^2}$ to account for the finite extension of the constituents.

>>>>

\centering
\begin{tabularx}{\textwidth}{cccccccc}
%\multicolumn{1}{l}{Mass number} & \multicolumn{1}{l}{Nucleus} & \multicolumn{1}{l}{Composition} & \multicolumn{1}{l}{$B_{E}$ (MeV)} & \multicolumn{1}{l}{rms radius of wavefunction (fm)} & \multicolumn{1}{l}{Refs.} 
 \hline \hline
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & Spin $J_{A}$ & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\ \hline
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}      \\ \hline
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &             &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &              &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &            & \cite{Davis:2005mb,Nemura:1999qp} \\ \hline
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &             & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8                       &                 & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1                      &           &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8                     &            & \cite{Davis:2005mb,Nemura:1999qp}\\ \hline \hline
\end{tabularx}
\caption{Properties of nuclei and hyper-nuclei. $B_{E}$ is the binding energy in MeV. The size of the nucleus is given in terms of the (charge) rms radius of the wavefunction, \rmsradius. The size parameter of the wave-function of the harmonic oscillator potential,  $r_{A}$, is chosen such that the measured/expected rms is approximately reproduced. Details are given in Appendix \ref{appendix:Sato}. Please note that proton rms charge radius $\lambda_{p}$ is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents.
 References are given in the last column. The spin of \hfourtwolambda\ is discussed in the text of~\cite{Nemura:1999qp}.}
\label{tab:nucleusradii}
\end{table}

@@

In contrast to the simple approach described in the previous section, a more advanced coalescence model takes into account the size of the particle emission source, as the coalescence probability naturally decreases for two nucleons with similar momenta that are produced far apart in configuration space. While there are several approaches to address this effect~\cite{Sato:1981ez, Nagle:1996vp, Bergstrom:1979gpv, PapersWithWignerCitedinUli}, we rely in our study on the formalism proposed in~\cite{Scheibl:1998tk}.

@@

\begin{equation}\label{eq:WaveHeinz}
 \varphi_{d}(\vec{r}) = (\pi r_{d}^2)^{-3/4} \exp\left(-{r^2 \over 2 r_{d}^2}\right) \;.
\end{equation}

@@

\begin{equation}
 \rmsradius^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
\end{equation}

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{4/3}  \rmsd$ for $A = 2$, $r_{3}= {\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{9/8} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).

@@

%%%%%%%%APPENDIX
\begin{appendix}
\section{Relation to the Sato-Yazaki coalescence model}\label{appendix:Sato}
%As discussed in~\cite{Nagle:1996vp}, 
The approach of Sato and Yazaki~\cite{Sato:1981ez} is based on a density matrix model and includes explicitly the system size dependence and wave-function dependence of the coalescence process albeit it assumes a sudden approximation when particles cease their interactions (sudden freeze-out) and thus neglects the collective expansion of the medium as in~\cite{Scheibl:1998tk}. Moreover, it assumes no correlation between different nucleons and no correlation between coordinates in space and momentum (in a heavy ion collisions, such correlations are consequence of hydrodynamical flow). 
%For the deuteron, the authors propose an expression for the coalescence momentum $p_{0}$ which equals
%\begin{equation}
%	{4 \over 3} \pi p_{0}^{3} = {3 \over 4} 2^{3/2} (4\pi)^{3/2} \left(\frac{\nu_{d}\nu}{\nu_d + \nu}\right)^{3/2}
%\end{equation}
%\noindent where the deuteron size parameter $\nu_d$ relates to the size parameter $r_{d}$ of the gaussian wave-function as $\nu_d = {2 \over r_{d}^2}$ and the size parameter $\nu$ to the rms $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$. 
\\In~\cite{Sato:1981ez}, the coalescence process to form a nucleus with mass number $A = Z + N$ is formulated in terms of the momentum per nucleon ($p$) as
%
\begin{equation}
\frac{\gamma_{A}}{\sigma_{A,0}} \frac{d^{3}\sigma_{A}}{d^{3}p} =  \left( {4 \over 3} \pi p_{0}^{3}\right)^{A-1}\frac{1}{Z! N!} \left(\frac{\gamma_{p}}{\sigma_{p,0}} \frac{d^{3}\sigma_{p}}{d^{3}p_{p}}\right)^{Z} \left(\frac{\gamma_{n}}{\sigma_{n,0}} \frac{d^{3}\sigma_{n}}{d^{3}p_{n}}\right)^{N} 
\end{equation} 
%
where $\gamma_{A}$ and $\gamma_{p,n}$ are the Lorentz factors for the nucleus and the nucleons, respectively. 
Assuming that the proton and neutron emission probabilities are equal and that $p_{p} \approx p_{n} \equiv p$, this expression relates to the $B_{A}$ as defined by our Lorentz invariant Eq.(\ref{eq:BA}) as

@@

\noindent For nuclei up to $A = 4$ and the non-relativistic case, Sato and Yazaki derive the following relations for the coalescence momentum $p_{0}$, 
%
\begin{align}
	A& =2&
	{4 \over 3} \pi p_{0}^{3}& ={3 \over 4}2^{3/2}(4\pi)^{3/2} \left(\frac{\nu_{2}\nu}{\nu_{2} + \nu}\right)^{3/2}\\
	A& =3&
	{1 \over 2} \left( {4 \over 3} \pi p_{0}^{3}\right)^{2}& ={1 \over 4} 3^{3/2} (4\pi)^{3} \left(\frac{\nu_{3}\nu}{\nu_{3} + \nu}\right)^{3}\\
	A& =4&  
	{1 \over 4} \left({4 \over 3} \pi p_{0}^{3}\right)^{3}& = {1 \over 16} 4^{3/2} (4\pi)^{9/2} \left(\frac{\nu_{4}\nu}{\nu_{4}+ \nu}\right)^{9/2}
\end{align}

\noindent where the size parameter $\nu$ relates to the rms radius $R_{rms}$ of the emission source as $\nu~=~\sqrt{3 \over 2 R_{rms}}$, and $\nu_{A}$ is the size parameter of the nucleus. 
\\Following the generalisation in~\cite{Nagle:1996vp}, we thus propose the following parameterisation for the coalescence parameter

\begin{eqnarray}
B_{A} &=& {2J_{A} + 1 \over 2^{A}} A^{3/2} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} {1 \over m^{A-1}} {1 \over A^{2}}  \\
\label{eq:SatoGeneralised}
           &=&  {2J_{A} + 1 \over 2^{A}} {1 \over m^{A-1}} {1 \over \sqrt{A}} (4\pi)^{{3\over2}(A-1)} \Bigl({\nu_{A}\nu \over \nu_{A}+ \nu}\Bigr)^{{3\over2}(A-1)} \;,
\end{eqnarray}

\noindent indicating with $J_{A}$ the spin of the nucleus.
Once again, the $\nu_{A}$ parameter corresponds to the size parameter of the nucleus wave-function, which is assumed to be gaussian (solution to the spherical harmonic oscillator potential) of the form~\cite{Sato:1981ez,Bergstrom:1979gpv}:

\begin{equation}\label{eq:SatoWave}
 \phi_{A} = C \exp\Bigl(-{1\over2} \nu_{A} \sum_{i=1}^{A}(\vec{x}_{i} - \vec{X})^2 \Bigr)
\end{equation}

\noindent with an appropriate normalisation factor $C$. 
\\We have also verified that our generalisation of Sato-Yazaki provided by Eq. \ref{eq:SatoGeneralised} and the expression derived from Heinz in Eq. \ref{eq:CA_general} become consistent in the limit $R_{rms} \approx R \rightarrow 0$ (point-like source) and $p_{\mathrm{T}} \rightarrow 0$ (static source), provided that one identifies $\nu_{A} = {2 / r_{A}^{2}}$. Incidentally, the same relation between $\nu_{A}$ and $r_{A}$ can be derived by a straightforward comparison of the nucleus wave-functions employed by the same authors \cite{Scheibl:1998tk,Sato:1981ez}.

The parameter $\nu_{A}$ is typically chosen such that the measured rms charge radius \rmsradius~is reproduced. The relation between \rmsradius~and $\nu_{A}$ is obtained by a transformation to the Jacobi variables and performing the integration (see Appendix \ref{appendix:integration}). In particular, one obtains for $A < 5$:

\begin{align}
	A& = 2 \qquad \qquad \nu_{2} = {3 \over {4\rmsd^2}}  \\
	A& = 3 \qquad \qquad \nu_{3} = {1 \over {\rmsthree^2}} \\
	A& = 4 \qquad \qquad \nu_{4} =  {9 \over {8\rmsfour^2}}
\end{align}
